---
title: "P8105_HW1_YX2953"
author: "VivianX"
date: "2024-09-21"
output: pdf_document
---

##Problem 1

```{r setup, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(palmerpenguins)
```

## Loading the Penguins Dataset

```{r load-data, echo=FALSE}
# Load the penguins dataset
data("penguins", package = "palmerpenguins")

head(penguins)
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

## Description of the Penguins Dataset

The penguins dataset provides data on three species of penguins (*Adelie*, *Chinstrap*, and *Gentoo*) along with various measurements. The dataset includes the following important variables:

- **species**: The species of the penguin (*Adelie*, *Chinstrap*, or *Gentoo*).
- **bill_length_mm**: Length of the penguin's bill in millimeters.
- **bill_depth_mm**: Depth of the penguin's bill in millimeters.
- **flipper_length_mm**: Length of the penguin's flipper in millimeters.
- **body_mass_g**: Body mass of the penguin in grams.
- **sex**: The sex of the penguin (male or female).

This dataset contains `nrow(penguins)` rows and `r ncol(penguins)` columns. The average flipper length is `mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

## Scatterplot of Flipper Length vs Bill Length

```{r scatterplot, echo=TRUE}
# Create scatterplot of flipper length vs. bill length, colored by species
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Scatterplot of Flipper Length vs Bill Length",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)")+
  theme_minimal()
```
## Save the Scatterplot

```{r save-plot, echo=TRUE}
# Export the scatterplot to the project directory
ggsave("penguin_scatterplot.png",width = 8,height=6)
```


##Problem 2


```{r}
# Load required package
library(tidyverse)
```


# Step 1: Create the data frame

```{r}
set.seed(123) # For reproducibility
df <- data.frame(
  random_sample = rnorm(10),                           
  # Random sample from Normal distribution
  logical_vector = rnorm(10) > 0,                      
  # Logical vector (TRUE if greater than 0)
  character_vector = sample(letters, 10),              
  # Random character vector
  factor_vector = factor(sample(c("A", "B", "C"), 10, replace = TRUE)) 
  # Factor vector with 3 levels
)
```

# Step 2: Attempt to take the mean of each variable
# Using pull() to extract the columns from the dataframe

```{r}
mean_numeric <- mean(pull(df, random_sample))          
# work
mean_logical <- mean(pull(df, logical_vector))         
# work (TRUE = 1, FALSE = 0)
mean_character <- mean(pull(df, character_vector))   
# fail, character vector has no numeric meaning
mean_factor <- mean(pull(df, factor_vector))         
# fail, factors are categorical
```

# Step 3: Coerce logical, character, and factor variables to numeric
# Apply as.numeric() to logical, character, and factor vectors

```{r}
df$numeric_logical <- as.numeric(df$logical_vector)    
# Logical: TRUE -> 1, FALSE -> 0
df$numeric_character <- as.numeric(df$character_vector) 
# Coercing characters to numeric (will result in NA)
df$numeric_factor <- as.numeric(df$factor_vector)     
# Coercing factors to their underlying integer levels
```


# Step 4: Output to understand what happens

```{r}
df
```

Findings:
**As it is shown in the result, when converted to numeric data type, the mean of the logical vector and factor vector can be calculated.**
* When converting factors to numeric, as.numeric() first converts the factors to integers.
* When converting logical variables, TRUE will be converted to 1 and FALSE will be converted to 0.
* However, when the converting object is character,
- If the character vector represents numbers, as.numberic() will convert them into numeric values.\
- If the character vector does not represent numbers, the function will return NA, then the mean fail to be calculated.
