---
title: "P8105_HW1_YX2953"
author: "VivianX"
date: "2024-09-21"
output: pdf_document
---


```{r setup, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(palmerpenguins)
```

## Loading the Penguins Dataset

```{r load-data, echo=FALSE}
# Load the penguins dataset
data("penguins", package = "palmerpenguins")

head(penguins)
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

## Description of the Penguins Dataset

The penguins dataset provides data on three species of penguins (*Adelie*, *Chinstrap*, and *Gentoo*) along with various measurements. The dataset includes the following important variables:

- **species**: The species of the penguin (*Adelie*, *Chinstrap*, or *Gentoo*).
- **bill_length_mm**: Length of the penguin's bill in millimeters.
- **bill_depth_mm**: Depth of the penguin's bill in millimeters.
- **flipper_length_mm**: Length of the penguin's flipper in millimeters.
- **body_mass_g**: Body mass of the penguin in grams.
- **sex**: The sex of the penguin (male or female).

This dataset contains `nrow(penguins)` rows and `r ncol(penguins)` columns. The average flipper length is `mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

## Scatterplot of Flipper Length vs Bill Length

```{r scatterplot, echo=TRUE}
# Create scatterplot of flipper length vs. bill length, colored by species
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Scatterplot of Flipper Length vs Bill Length",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)")+
  theme_minimal()
```
## Save the Scatterplot

```{r save-plot, echo=TRUE}
# Export the scatterplot to the project directory
ggsave("penguin_scatterplot.png",width = 8,height=6)
```